Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond

### 2024-02-12 outputs/paper/paper.qmd
update

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-polscatter-table
#| tbl-cap: "US presidents"

# Create a dataframe with information about the Presidents and their respective parties
presidents <- data.frame(
  president = c("Ronald Reagan", "George H. W. Bush", "Bill Clinton", "George W. Bush", "Barack Obama", "Donald Trump", "Joe Biden"),
  party = c("Republican", "Republican", "Democratic", "Republican", "Democratic", "Republican", "Democratic"),
  start_year = c(1981, 1989, 1993, 2001, 2009, 2017, 2021),
  end_year = c(1989, 1993, 2001, 2009, 2017, 2021, NA) # NA for current President
)

head(presidents)

```
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-polscatter-graph
#| fig-cap: "Trend in US Birth Rates with political party in their presidential mandate"

@@

@@

## Future Research
It might be worth investigating some other aspects of the society such as political demographic, immigration law, and enforcement. Based on trend in

>>>>

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-polscatter-graph
#| fig-cap: "Trend in US Birth Rates with political party in their presidential mandate"

@@

@fig-polscatter-graph draw multiple trend lines

@@

## Future Research
It might be worth investigating some other aspects of the society such as political demographic, immigration law, and enforcement. Based on trend in @fig-polscatter-graph, it is worth to delve into immigration law, campaign promises for their presidential mandates.
